---
title: "gameGA: Browser interface"
output:
  html_document: default
header-includes:
linestretch: 1
runtime: shiny
---

```{r, echo=FALSE}
library(gamesGA)
library(shiny)
library(rhandsontable)
```

********************************************************************************

> **The [gameGA](https://github.com/bradduthie/gamesGA) R package simulates a genetic algorithm for finding adaptive strategies in sequentially played rounds of any two by two sequential payoff matrix game iterated between players. Below, the embedded [shiny](https://shiny.rstudio.com/) application recognises user inputs in the `games_ga()` function and returns a table showing surviving strategies and their corresponding frequencies.**

> [See here](#help) for instructions on [inputs](#help) and interpretion of [output](#out). To install the `gamesGA` package, [see here](https://github.com/bradduthie/gamesGA/blob/master/README.md).

********************************************************************************

<br>

```{r, echo=FALSE}
inputPanel(
    
    numericInput("CC", label = "CC", 3, width="50%"),
    numericInput("DC", label = "DC", 5, width="50%"),
    numericInput("CD", label = "CD", 0, width="50%"),
    numericInput("DD", label = "DD", 1, width="50%"),
    numericInput("RnD", label = "Rounds", 100, width="50%"),
    numericInput("Gen", label = "Generations", 250, width="50%"),
    numericInput("Cro", label = "Pr(Crossover)", 0.05, width="50%"),
    numericInput("mu", label = "Pr(Mutation)", 0.05, width="50%"),    
    
    style='width: 900px; height: 150px'
)
```

<br>
    
```{r, echo=FALSE}
renderTable({
    cc <- input$CC;
    dc <- input$DC;
    cd <- input$CD;
    dd <- input$DD;
    rd <- input$RnD;
    gn <- input$Gen;
    co <- input$Cro;
    mu <- input$mu;

    game_res <- games_ga(CC = cc, DC = dc, CD = cd, DD = dd, rounds = rd,
                         generations = gn, cross_prob = co, 
                         mutation_prob = mu, num_opponents = 100); 
    
    max_geno <- dim(game_res$genos)[1];

    final_table <- game_res$genos[1:max_geno,];
    
}, include.rownames=TRUE)
```

<br>

********************************************************************************

<br>

<a name="help">Input variables</a>
--------------------------------------------------------------------------------

A list of all of the inputs that can be used in the embedded application above is presented below with explanation:

 - `CC` The payoff that the focal player receives if the focal player and the opponent both cooperate
 - `DC` The payoff that the focal player receives if the focal player defects but the opponent cooperates
 - `CD` The payoff that the focal player receives if the focal player cooperates but the opponent defects
 - `DD` The payoff that the focal player receives if the focal player and the opponent both defect
 - `Rounds` The number of rounds a focal player plays against each opponent
 - `Generations` The number of generations the genetic algorithm is allowed to run before producing the output of strategies. By default, **each strategy will compete against all 100 strategies in the population (including itself)**
 - `Pr(Cossover)` The probability that a crossover event occurs at any given locus between a focal player and a randomly selected player in the population
 - `Pr(Mutation)` For each locus of every player, the probability that a mutation occurs in a generation
 
 The inputs `CC`, `DC`, `CD`, and `DD` can be visualised as the payoffs that a focal individual receives on a standard $2 \times 2$ payoff matrix, shown below.

|                         | Opponent cooperates | Opponent defects |
|-------------------------|---------------------|------------------|
| Focal player cooperates |   **CC**            |  **CD**          |
| Focal player defects    |   **DC**            |  **DD**          |

Hence, `gamesGA` does not (yet) model non-symmetric payoffs.

<br>

<a name="out">Table output</a>
--------------------------------------------------------------------------------

In the above output table, each row corresponds to a unique strategy that is present in the population after `Generations` of simulated evolution. The first eight columns in the table correspond to the response of a focal strategy given the history of an opponent. For example, in the first column, **C C C** corresponds to a history of three previous rounds of an opponent playing **C** (cooperate). The row element in this column therefore indicates the focal strategy's response (**C** cooperation, or **D** defect) if its opponent has coopereated three times in a row. The nineth column indicates the evolved strategy that a focal player adopts for their first round move (for second and third round moves, see how the [code](https://github.com/bradduthie/gamesGA/blob/master/src/fitness.c) handles the reduced information). Finally, the **Final %** column indicates the perecentage of individuals in the population adopting the row strategy.
